Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-02-02 parts/intro.tex
typos & update new notations

\paragraph*{Sets}
If $A$ is a finite set,
$|A|$ is the cardinality of $A$
and $\powerset(A)$ is the power set of $A$.
$\sN$ is the set of natural numbers,
$\sN^* = \sN \setminus \{ 0 \}$ is the set of positive natural numbers,
$\sNN = \sN \setminus \{ 0, 1 \}$ is the set of natural numbers strictly greater than 1,
and $\segm{x}{y} = \{ x, x+1, \dots, y-1, y \}$ is the set of natural numbers from $x$ to $y$ included.
The Cartesian product is denoted $\times$;
if $z$ is a tuple of $n$ components, $\toset{z}$ denotes the corresponding set:
$\toset{z} = \{z_1, \cdots, z_n\}$.

@@

\paragraph*{Digraph}
If $(V,E)$ is a directed graph, $V$ are the nodes, $E \subset V\times V$ the edges,
the children of a node $n$ are given by
$\childs: V \to \powerset(V)$, with
$\childs(n) \DEF \{ m\in V\mid (n,m)\in E\}$;
its parents are given by
$\parents: V \to \powerset(V)$ with
$\parents(n) \DEF \{ m\in N\mid (m,n)\in E\}$;
and its descendants are give by
$\conn_{(V,E)}(n)$ which is the least fixed point containing $n$
of the function
$\f{f}\conn:\powerset(N)\to \powerset(N)$
with $\f{f}\conn(W) \DEF \bigcup_{m\in W} \childs(m)$.

>>>>

\paragraph*{Sets}
If $A$ is a finite set,
$|A|$ is the cardinality of $A$
and $\powerset(A)$ is the power set of $A$.
$\sN$ is the set of natural numbers,
$\sN^* = \sN \setminus \{ 0 \}$ is the set of positive natural numbers,
$\sNN = \sN \setminus \{ 0, 1 \}$ is the set of natural numbers strictly greater than 1,
and $\segm{x}{y} = \{ x, x+1, \dots, y-1, y \}$ is the set of natural numbers from $x$ to $y$ included.
The Cartesian product of sets is denoted by $\times$;
if $z$ is a tuple of $n$ components, $\toset{z}$ denotes the corresponding set:
$\toset{z} = \{z_1, \cdots, z_n\}$.

@@

\paragraph*{Digraph}
If $(V,E)$ is a directed graph whose $V$ are the nodes and $E \subseteq V\times V$ the edges,
the children of a node $n$ are given by
$\childs: V \to \powerset(V)$, with
$\childs(n) \DEF \{ m\in V\mid (n,m)\in E\}$;
its parents are given by
$\parents: V \to \powerset(V)$ with
$\parents(n) \DEF \{ m\in N\mid (m,n)\in E\}$;
and its successors are given by
$\conn_{(V,E)}(n)$ which is the least fixed point containing $n$
of the function
$\f{f}\conn:\powerset(V)\to \powerset(V)$
with $\f{f}\conn(W) \DEF \bigcup_{m\in W} \childs(m)$.

### 2015-02-02 parts/sa.tex
typos & update new notations

\modLP{%
We present a static analysis that takes as input an AAN
$\PH = (\PHs; \PHl; \PHa)$,
an initial state, and a local state of an automata in $\PHs$, for identifying sufficient conditions
that ensure the existence of a scenario starting from the initial state and leading to a state
where the given local state is present.}

@@

Given one initial objective, one could then recursively refine the objective into objective
sequences following its bounce sequences \cite{PMR12-MSCS}:
the refinement of objective $P$ with $\zeta\in\BS(P)$ would consists in prepending to $P$ the
objectives leading to the hitters of the actions in $\zeta$, in the same sequential order;
the generalisation of the refinement to an objective sequence would require to consider all possible
interleaving between the refinements.

These refinements can be summarized compactly with a so-called Local Causality Graph (LCG).
Given an initial context $\ctx$ and a local state $p\in\Proc$,
A LCG $\cwB = (\cwV, \cwE)$
is a digraph where $\cwV \subseteq \Proc\cup \Obj \cup \Sol \cup \sSol$ is the set of vertices
where $\sSol=\powerset(\Proc)$ and $\Sol=\Obj\times\powerset(\sSol)$
and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges
(\pref{def:lcg}).
A node in $\Obj$ represents an objective that have to be refined.
Such a node can then be related to nodes in $\Sol$ which represents a set of hitter set of a
bounce sequence of the objective:
given an objective $P$, if $\zeta\in\BS(P)$, $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid
n\in\indexes\zeta \}$, then $P$ is related to $\langle P, \abstr\zeta\rangle\in\Sol$
(\pref{def:lcg}-3).
Given a node $\langle P,\abstr\zeta\rangle\in\cwV\cap\Sol$, for each $ps\in\abstr\zeta$,
it is related to a node $ps\in\sSol$
(\pref{def:lcg}-4).
A node $ps\in\sSol$ is then related to each $a\in\Proc$
(\pref{def:lcg}-5).
Given a node $a_i\in\cwV\cap\Proc$, for each $a_j\in\ctx$ or $a_j\in\cwV\cap\Proc$,
it is related to an objective $\obj{a_j}{a_i}$
(\pref{def:lcg}-2).
Finally, given a node $\obj{a_j}{a_i}\in\cwV\cap\Obj$,
if a local state $a_k\neq a_i$ is in its descendants (given by
$\conn_{(\cwBNodes,\cwBEdges)}(\obj{a_j}{a_i})$), then
$\obj{a_j}{a_i}$ is related to $\obj{a_k}{a_i}$ in the LCG
(\pref{def:lcg}-6).

\begin{definition}
\label{def:lcg}
Given a context $\ctx$ and a local state $p\in \Proc$,
the Local Causality Graph (LCG) for reachability under-approximation
$\cwB \DEF (\Bv, \Be)$
with
$\cwBNodes \subseteq \Proc \cup \Obj \cup \NSol \cup \sSol$
and
$\cwBEdges \subseteq \cwBNodes \times \cwBNodes$,
is the smallest graph such that:
\begin{enumerate}
\item
$p \in \cwBNodes$
\item
$a_i\in\cwBNodes\cap\Proc \Leftrightarrow \{ (a_i,\obj{a_j}{a_i}) \mid
a_j\in\ctx \vee a_j\in\cwBNodes\cap\Proc)
\}\subseteq\cwBEdges$
\item
$P\in\cwBNodes\cap\Obj \Leftrightarrow 
	\{ (P,\langle P,\abstr \zeta\rangle) \mid \zeta\in\BS(P) \}\subseteq\cwBEdges$
\item
$\langle P, nls \rangle\in\cwBNodes\cap\NSol \Leftrightarrow
	\{ (\langle P,nls\rangle, ls) \mid ls\in nls \}\subseteq\cwBEdges$
\item
$ls \in\cwBNodes\cap\sSol \Leftrightarrow
	\{ (ls, a_i) \mid a_i\in ls \}\subseteq\cwBEdges$
\item
$\obj{a_i}{a_j}\in \cwBNodes\cap\Obj \Rightarrow 
	\{(\obj{a_i}{a_j},\obj{a_k}{a_j}) \mid a_k\neq a_j,$
\\
\hspace*{4cm}
$a_k\in \conn_{(\cwBNodes,\cwBEdges)}(\langle\obj{a_i}{a_j},\abstr\zeta\rangle),$
\\
\hspace*{4cm}
$\zeta\in\BS(\obj{a_i}{a_j}) \}\subset\cwBEdges$
\end{enumerate}
with $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid n\in\indexes\zeta \}$.
\end{definition}

@@

A node $x$ of the LCG in $\sSol$ is \emph{independent} (\pref{def:coherent}) if for each local state
$a_i\in x$, none of the other local state $b_j\in x$ have a local state of automaton $a$ different
than $a_i$ in their descendants.
This criteria ensures that once a local state in $x$ has been reached, reaching another local state
in $x$ should not require to change the first local state.

\begin{definition}[Independent synchronisations]
\label{def:coherent}
  In a LCG $\cwB = (\Bv, \Be)$,
  a node $x \in \Bv\cap\sSol$ is \emph{independent} if and only if
  for each $a_i\in x$,
  for each $b_j\in x, b_j\neq a_i$,
  $a_k \in\conn_{\cwB}(x) \cap \Proc \Rightarrow a_k = a_i$.
\end{definition}

The intuition is the following.
Given a state $s\subset\ctx$, we recursively refine the initial objective (reaching $p$ from the initial
state) according to its children.
As the LCG is acyclic, such a recursion always terminates, and as all the objective nodes have at
least one child, it never get stuck.
The refinement of an objective node $\obj{a_i}{a_j}$ acts as follows:
if the node has another objective node $\obj{a_k}{a_j}$ as child, we first refine the objective
$\obj{a_i}{a_k}$ (which, by construction, is necessarily in the LCG)
and then will refine the objective $\obj{a_k}{a_j}$.
If the objective nodes has only nodes in $\Sol$ (bounce sequences), one is picked arbitrarily.
If $\langle P, nls\rangle$ is the chosen node,
by construction there exists $\zeta\in\BS(P)$ such that $\abstr\zeta = nls \in \powerset(\sSol)$.
If $\zeta = \emptyseq$ (for instance in the case when $a_i = a_j$), the recursion stops and we
continue to the next stage.
Otherwise, for each $n\in\indexes\zeta$,
for each $b_i \in\PHhitter(\zeta_n)$,
we refine the objective $\obj{b_j}{b_i}$ where $b_j$ is the state of $b$ in the current state.
By induction, $\obj{b_j}{b_i}$ is a child of $b_i$ in the LCG of \pref{def:lcg}.
Then, we know (by induction) that the current state of $b$ is $b_i$.
After having repeated this procedure for each $b_i\in\PHhitter(\zeta_n)$,
because all the nodes in $\sSol$, and in particular $\PHhitter(\zeta_n)$, are independent,
we know that all the local states in $\PHhitter(\zeta_n)$ are in the current state.
In addition, we know that the state of automaton $a$ has remained unchanged, otherwise
$\obj{a_i}{a_j}$ would have an objective child.
Hence, the action $\zeta_n$ is playable in the current state.
We apply this action, modifying the state of $a$ to $a_j$ and continue to the next stage.
At the end, this recursive procedures builds a scenario from $s\subset\ctx$ to a state containing $p$.

@@

We note furthermore that the method does not require any completeness of the bounce sequences
$\BS$.
Therefore, in order to reduce the number of bounce sequences to consider, and potentially removing
cycles and non-satisfying nodes,
one can consider only a sub-set of, or single, bounce sequences for each objectives.
However, such an approach would imply to enumerate all possible combinations of bounce sequences
subsets, hence being exponential in the number of objectives having at least two bounce sequences.

\begin{example}
  \moda{%
  If we confider the AAN of \pref{fig:ph-livelock},
  from the initial state $\PHstate{a_1, b_0, c_0}$ depicted,
  the under-approximation given in \pref{th:approxinf}
  does not conclude regarding the reachability of $c_1$.
  This is due to the fact that the node $\{ a_1, b_1 \} \in \Bv \cap \sSol$
  is not coherent because of its successor $a_0$ (and $b_0$).
  (However, from the inconclusiveness of \pref{th:approxinf},
  one cannot conclude about the unreachability of $c_1$.
  Such analysis should be driven for instance
  with over-approximation methods developed in~\cite{PMR12-MSCS}.)
  }%

@@

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b10s) edge (nb10s)
    (b00) edge (b00s)
    (b00s) edge (nb00s)
    (b1) edge (b01) edge (b11)
    (b01) edge (b01s)
    (b01s) edge (b01ss)
    (b01ss) edge (a0)
    (b11) edge (b11s)
    (b11s) edge (nb11s)
    ;
    \end{tikzpicture}
  \caption{
  \label{fig:sa-livelock}
    The saturated graph of local causality of the AAN in \pref{fig:ph-livelock}
    for the objective $\w = \PHobj{c_0}{c_1}$
    and the initial context $\ctx = \PHstate{a_1, b_0, c_0}$.
    Elements in $\Proc$ are represented by rectangular nodes,
    elements in $\Sol$ are represented by circle nodes,
    and elements in $\sSol$ and $\Obj$ are the remaining borderless nodes.
    \pref{th:approxinf} is inconclusive on this example as node $\{ a_1, b_1 \}$
    is not coherent (see \pref{def:coherent}).
    Indeed, $a_0 \in \Proc$ is a successor of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$
    (and the same also stands for $b_0$).
  }
\end{figure}
\end{example}

@@

In order to check the reachability of a global state $s \in \PHl$,
let $\PH = (\PHs, \PHl, \PHh)$ be an AAN.
We define a new AAN $\PH' = (\PHs', \PHl', \PHh')$ with:
$\PHs' = \PHs \cup \{ \reach \}$, $\PHl' = \PHl \times \PHl_\reach$,
where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
and $\PHh' = \PHh \cup \{ \PHhit{\toset{s}}{\reach_0}{\reach_1} \}$.
Given an initial context $\ctx$, the reachability of $s$ in $\PH$
is equivalent to the concretisation of $\PHobjp{\reach}{0}{1}$ in $\PH'$
from the initial context $\ctx \cup \{ \reach_0 \}$,
which can be efficiently under-approximated using \pref{th:approxinf}.

>>>>

\modLP{%
We present a static analysis that takes as input an AAN
$\PH = (\PHs; \PHl; \PHa)$,
an initial state, and a local state of an automaton in $\PHs$, for identifying sufficient conditions
that ensure the existence of a scenario starting from the initial state and leading to a state
where the given local state is present.}

@@

Given one initial objective, one could then recursively refine the objective into objective
sequences following its bounce sequences \cite{PMR12-MSCS}:
the refinement of objective $P$ with $\zeta\in\BS(P)$ would consists in prepending to $P$ the
objectives leading to the hitters of the actions in $\zeta$, in the same sequential order;
the generalization of the refinement to an objective sequence would require to consider all possible
interleaving between the refinements.

These refinements can be summarized compactly with a so-called Local Causality Graph (LCG).
Given an initial context $\ctx$ and a local state $p\in\Proc$,
A LCG $\cwB = (\cwV, \cwE)$
is a digraph where $\cwV \subseteq \Proc\cup \Obj \cup \Sol \cup \sSol$ is the set of vertices
where $\sSol=\powerset(\Proc)$ and $\Sol=\Obj\times\powerset(\sSol)$
and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges
(\pref{def:lcg}).
A node in $\Obj$ represents an objective that have to be refined.
Such a node can then be related to nodes in $\Sol$ which represents a set of hitter set of a
bounce sequence of the objective:
given an objective $P$, if $\zeta\in\BS(P)$, $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid
n\in\indexes\zeta \}$, then $P$ is related to $\langle P, \abstr\zeta\rangle\in\Sol$
(\pref{def:lcg}-\ref{lcg-obj-sol}).
Given a node $\langle P,\abstr\zeta\rangle\in\cwV\cap\Sol$, for each $ps\in\abstr\zeta$,
it is related to a node $ps\in\sSol$
(\pref{def:lcg}-\ref{lcg-sol-sync}).
A node $ps\in\sSol$ is then related to each $a\in\Proc$
(\pref{def:lcg}-\ref{lcg-sync-ls}).
Given a node $a_i\in\cwV\cap\Proc$, for each $a_j\in\ctx$ or $a_j\in\cwV\cap\Proc$,
it is related to an objective $\obj{a_j}{a_i}$
(\pref{def:lcg}-\ref{lcg-ls-obj}).
Finally, given a node $\obj{a_j}{a_i}\in\cwV\cap\Obj$,
if a local state $a_k\neq a_i$ is in its successors (given by
$\conn_{(\cwBNodes,\cwBEdges)}(\obj{a_j}{a_i})$), then
$\obj{a_j}{a_i}$ is related to $\obj{a_k}{a_i}$ in the LCG
(\pref{def:lcg}-\ref{lcg-conn}).

\begin{definition}
\label{def:lcg}
Given a context $\ctx$ and a local state $p\in \Proc$,
the Local Causality Graph (LCG) for reachability under-approximation
$\cwB \DEF (\Bv, \Be)$
with
$\cwBNodes \subseteq \Proc \cup \Obj \cup \NSol \cup \sSol$
and
$\cwBEdges \subseteq \cwBNodes \times \cwBNodes$,
is the smallest graph such that:
\begin{enumerate}
\item
$p \in \cwBNodes$
\item
$a_i\in\cwBNodes\cap\Proc \Leftrightarrow \{ (a_i,\obj{a_j}{a_i}) \mid
a_j\in\ctx \vee a_j\in\cwBNodes\cap\Proc)
\}\subseteq\cwBEdges$
\label{lcg-ls-obj}
\item
$P\in\cwBNodes\cap\Obj \Leftrightarrow 
	\{ (P,\langle P,\abstr \zeta\rangle) \mid \zeta\in\BS(P) \}\subseteq\cwBEdges$
\label{lcg-obj-sol}
\item
$\langle P, nls \rangle\in\cwBNodes\cap\NSol \Leftrightarrow
	\{ (\langle P,nls\rangle, ls) \mid ls\in nls \}\subseteq\cwBEdges$
\label{lcg-sol-sync}
\item
$ls \in\cwBNodes\cap\sSol \Leftrightarrow
	\{ (ls, a_i) \mid a_i\in ls \}\subseteq\cwBEdges$
\label{lcg-sync-ls}
\item
$\obj{a_i}{a_j}\in \cwBNodes\cap\Obj \Rightarrow 
	\{(\obj{a_i}{a_j},\obj{a_k}{a_j}) \mid a_k\neq a_j,$
\label{lcg-conn}
\\
\hspace*{4cm}
$a_k\in \conn_{(\cwBNodes,\cwBEdges)}(\langle\obj{a_i}{a_j},\abstr\zeta\rangle),$
\\
\hspace*{4cm}
$\zeta\in\BS(\obj{a_i}{a_j}) \}\subset\cwBEdges$
\end{enumerate}
with $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid n\in\indexes\zeta \}$.
\end{definition}

@@

A node $x$ of the LCG in $\sSol$ is \emph{independent} (\pref{def:coherent}) if for each local state
$a_i\in x$, none of the other local state $b_j\in x$ have a local state of automaton $a$ different
than $a_i$ in their successors.
This criteria ensures that once a local state in $x$ has been reached, reaching another local state
in $x$ should not require to change the first local state.

\begin{definition}[Independent synchronizations]
\label{def:coherent}
  In a LCG $\cwB = (\Bv, \Be)$,
  a node $x \in \Bv\cap\sSol$ is \emph{independent} if and only if
  for each $a_i\in x$,
  for each $b_j\in x, b_j\neq a_i$,
  $a_k \in\conn_{\cwB}(b_j) \cap \Proc \Rightarrow a_k = a_i$.
\end{definition}

The intuition is the following.
Given a state $s\subset\ctx$, we recursively refine the initial objective
(which is: reaching $p$ from the initial state) according to its children.
As the LCG is acyclic, such a recursion always terminates, and as all the objective nodes have at
least one child, it never gets stuck.
The refinement of an objective node $\obj{a_i}{a_j}$ acts as follows:
if the node has another objective node $\obj{a_k}{a_j}$ as child, we first refine the objective
$\obj{a_i}{a_k}$ (which, by construction, is necessarily in the LCG)
and then we refine the objective $\obj{a_k}{a_j}$.
If the objective node has only successors in $\Sol$ (bounce sequences), one is picked arbitrarily.
If $\langle P, nls\rangle$ is the chosen node,
by construction there exists $\zeta\in\BS(P)$ such that $\abstr\zeta = nls \in \powerset(\sSol)$.
If $\zeta = \emptyseq$ (for instance in the case when $a_i = a_j$), the recursion stops and we
continue to the next stage.
Otherwise, for each $n\in\indexes\zeta$,
for each $b_i \in\PHhitter(\zeta_n)$,
we refine the objective $\obj{b_j}{b_i}$ where $b_j$ is the state of $b$ in the current state.
By induction, $\obj{b_j}{b_i}$ is a child of $b_i$ in the LCG of \pref{def:lcg}.
Then, we know (by induction) that the current state of $b$ is $b_i$.
After having repeated this procedure for each $b_i\in\PHhitter(\zeta_n)$,
because all the nodes in $\sSol$, and in particular $\PHhitter(\zeta_n)$, are independent,
we know that all the local states in $\PHhitter(\zeta_n)$ are in the current state.
In addition, we know that the state of automaton $a$ has remained unchanged, otherwise
$\obj{a_i}{a_j}$ would have an objective child.
Hence, the action $\zeta_n$ is playable in the current state.
We can thus apply this action, modifying the state of $a$ to $a_j$ and continue to the next stage.
In the end, this recursive procedures builds a scenario from $s\subset\ctx$ to a state containing $p$.

@@

We note furthermore that the method does not require any completeness of the bounce sequences
$\BS$.
Therefore, in order to reduce the number of bounce sequences to consider, and potentially removing
cycles and non-satisfying nodes,
one can consider only a sub-set of bounce sequences
(and in particular: a single bounce sequence) for each objective.
However, such an approach would imply to enumerate all possible combinations of bounce sequences
subsets, hence being exponential in the number of objectives having at least two bounce sequences.

\begin{example}
  \moda{%
  If we confider the AAN of \pref{fig:ph-livelock},
  from the initial state $\PHstate{a_1, b_0, c_0}$ depicted,
  the under-approximation given in \pref{th:approxinf}
  does not conclude regarding the reachability of $c_1$.
  This is due to the fact that the node $\{ a_1, b_1 \} \in \Bv \cap \sSol$
  is not independent because of its successor $a_0$ (and $b_0$).
  (However, from the inconclusiveness of \pref{th:approxinf},
  one cannot conclude about the unreachability of $c_1$.
  Such analysis should be driven for instance
  with over-approximation methods developed in~\cite{PMR12-MSCS}.)
  }%

@@

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b10s) edge (nb10s)
    (b00) edge (b00s)
    (b00s) edge (nb00s)
    (b1) edge (b01) edge (b11)
    (b01) edge (b01s)
    (b01s) edge (b01ss)
    (b01ss) edge (a0)
    (b11) edge (b11s)
    (b11s) edge (nb11s)
    ;
    \end{tikzpicture}
  \caption{
  \label{fig:sa-livelock}
    The saturated graph of local causality of the AAN in \pref{fig:ph-livelock}
    for the objective $\w = \PHobj{c_0}{c_1}$
    and the initial context $\ctx = \PHstate{a_1, b_0, c_0}$.
    Elements in $\Proc$ are represented by rectangular nodes,
    elements in $\Sol$ are represented by circle nodes,
    and elements in $\sSol$ and $\Obj$ are the remaining borderless nodes.
    \pref{th:approxinf} is inconclusive on this example as node $\{ a_1, b_1 \}$
    is not independent (see \pref{def:coherent}).
    Indeed, $a_0 \in \Proc$ is a successor of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$
    (and the same also stands for $b_0$).
  }
\end{figure}
\end{example}

@@

In order to check the reachability of a global state $s \in \PHl$,
let $\PH = (\PHs, \PHl, \PHh)$ be an AAN.
We define a new AAN $\PH' = (\PHs', \PHl', \PHh')$ with:
$\PHs' = \PHs \cup \{ \reach \}$, $\PHl' = \PHl \times \PHl_\reach$,
where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
and $\PHh' = \PHh \cup \{ \PHhit{\toset{s}}{\reach_0}{\reach_1} \}$.
Given an initial context $\ctx$, the reachability of $s$ in $\PH$
is equivalent to the concretization of $\PHobjp{\reach}{0}{1}$ in $\PH'$
from the initial context $\ctx \cup \{ \reach_0 \}$,
which can be efficiently under-approximated using \pref{th:approxinf}.

### 2015-02-02 parts/suppl-sa.tex
typos & update new notations

@@

Let $ps \in \Bv \cap \sSol$ be a set of hitters
and suppose all of its successors are concretisable.
We first want to demonstrate that
there exists a scenario that activate all the local states it contains.
We label all local states of $ps$ by an integer: $ps = \{ p_n \}_{n \in \indexes{ps}}$.
Let us prove by induction that for all $n \in \indexes{ps}$, there exists a scenario $\delta_n$ so that:
$\forall i \in \segm{1}{n}, \PHget{(s \PHplay \delta_n)}{\PHsort(p_i)} = p_i$.
\begin{itemize}
  \item It is straightforward for $\delta_0 = \varepsilon$.
  \item Suppose such $\delta_n$ exists and let $q = \PHget{(s \PHplay \delta_n)}{\PHsort(p_{n+1})}$.
    By construction, $p_{n+1} \in \Bv \cap \Proc$ is a direct successor of $ps$.
    Furthermore, by hypothesis, $ps$ is coherent (see \pref{def:coherent}).
    This means that amongst all the successors in $\Proc$ of $p_{n+1}$,
    there does not exist a local state $b_j$ to that
    $\exists b_k \in ps, \PHsort(b_j) = \PHsort(b_k) \wedge b_j \neq b_k$;
    in other words, the resolution of $p_{n+1}$ does not require a local state
    that may change the other local states of the set $ps$.
    Therefore, there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{q}{p_{n+1}})$,
    so that $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
    We denote then: $\delta_{n+1} = \delta_n \play \delta'$.
\end{itemize}
Therefore, $\delta = \delta_{\card{ps}}$ exists, and given its properties, we have:
$\forall i \in \segm{1}{\card{ps}}, \PHget{(s \PHplay \delta)}{\PHsort(p_{i})} = p_{i}$.

@@

  \item Suppose all successors objectives of $P$ are concretisable.
    If $\exists (P, Q) \in \Bee{\Obj}{\Obj}$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    Else, by \pref{def:maxCont}, the concretisations of the successors of $P$ require no local state of automaton $\PHsort(P)$.
      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bee{\Obj}{\Sol}$.
      We show by induction that for all $n \in \indexes{\zeta}$, there is a scenario $\delta_n$ so that $\PHget{(s \PHplay \delta_n)}{\PHsort(P)} = \PHbounce(\zeta_n)$.
      \begin{itemize}
%        \item[$\circ$] If $\zeta = \emptyseq$, then trivially, $\delta = \emptyseq$.
        \item[$\circ$] Suppose that $\delta_n$ exists and let $\zeta_n = \PHhit{A}{a_j}{a_k}$.
        By construction, there exists $A \in \Bv \cap \sSol$
        amongst the direct successors of $\aZ$.
        By the first result of this demonstration,
        there exists a scenario $\delta'$ in $s \play \delta_n$ so that
        $\forall a_i \in A, \PHget{(s \play \delta_n \PHplay \delta')}{a} = a_i$.
        Therefore, $\zeta_n$ is playable in $s \play \delta_n \PHplay \delta'$,
        and $\delta_{n+1} = \delta_n \concat \delta' \concat \zeta_n$.
      \end{itemize}
      Thus, $\delta_{|\zeta|} \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
\end{itemize}
Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq
\emptyset$ (\pref{lem:uconcr-ctx}).
\end{proofapproxinf}

>>>>

\todo{Check with the new notations ($\muconcr$, $\procs$)}

@@

Let $ps \in \Bv \cap \sSol$ be a set of hitters
and suppose all of its successors are concretizable.
We first want to demonstrate that
there exists a scenario that activate all the local states it contains.
We label all local states of $ps$ by an integer: $ps = \{ p_n \}_{n \in \indexes{ps}}$.
Let us prove by induction that for all $n \in \indexes{ps}$, there exists a scenario $\delta_n$ so that:
$\forall i \in \segm{1}{n}, \PHget{(s \PHplay \delta_n)}{\PHsort(p_i)} = p_i$.
\begin{itemize}
  \item It is straightforward for $\delta_0 = \varepsilon$.
  \item Suppose such $\delta_n$ exists and let $q = \PHget{(s \PHplay \delta_n)}{\PHsort(p_{n+1})}$.
    By construction, $p_{n+1} \in \Bv \cap \Proc$ is a child of $ps$.
    Furthermore, by hypothesis, $ps$ is independent (see \pref{def:coherent}).
    This means that amongst all the successors in $\Proc$ of $p_{n+1}$,
    there does not exist a local state $b_j$ to that
    $\exists b_k \in ps, \PHsort(b_j) = \PHsort(b_k) \wedge b_j \neq b_k$;
    in other words, the resolution of $p_{n+1}$ does not require a local state
    that may change the other local states of the set $ps$.
    Therefore, there exists $\delta' \in \muconcr_{s \PHplay \delta_n}(\PHobj{q}{p_{n+1}})$,
    so that $\forall i \in \segm{1}{n+1}$, $\PHget{(s \PHplay \delta_n \PHplay \delta')}{\PHsort(p_{i})} = p_{i}$.
    We denote then: $\delta_{n+1} = \delta_n \play \delta'$.
\end{itemize}
Therefore, $\delta = \delta_{\card{ps}}$ exists, and given its properties, we have:
$\forall i \in \segm{1}{\card{ps}}, \PHget{(s \PHplay \delta)}{\PHsort(p_{i})} = p_{i}$.

@@

  \item Suppose all successors objectives of $P$ are concretizable.
    If $\exists (P, Q) \in \Bee{\Obj}{\Obj}$, then by hypothesis,
      $\muconcr_{s}(\obj{\PHtarget(P)}{\PHtarget(Q)} \concat Q) \neq \emptyset$, thus
      $\muconcr_{s}(P) \neq \emptyset$.
    Else, by \pref{def:lcg}-\ref{lcg-conn}, the concretizations of the successors of $P$ require no local state of automaton $\PHsort(P)$.
      Furthermore, there exists $\zeta \in \BS(P)$ so that $(P, \aZ) \in \Bee{\Obj}{\Sol}$.
      We show by induction that for all $n \in \indexes{\zeta}$, there is a scenario $\delta_n$ so that $\PHget{(s \PHplay \delta_n)}{\PHsort(P)} = \PHbounce(\zeta_n)$.
      \begin{itemize}
%        \item[$\circ$] If $\zeta = \emptyseq$, then trivially, $\delta = \emptyseq$.
        \item[$\circ$] Suppose that $\delta_n$ exists and let $\zeta_n = \PHhit{A}{a_j}{a_k}$.
        By construction, there exists $A \in \Bv \cap \sSol$
        amongst the children of $\aZ$.
        By the first result of this demonstration,
        there exists a scenario $\delta'$ in $s \play \delta_n$ so that
        $\forall a_i \in A, \PHget{(s \play \delta_n \PHplay \delta')}{a} = a_i$.
        Therefore, $\zeta_n$ is playable in $s \play \delta_n \PHplay \delta'$,
        and $\delta_{n+1} = \delta_n \concat \delta' \concat \zeta_n$.
      \end{itemize}
      Thus, $\delta_{|\zeta|} \in \muconcr_s(P)$. % and $\ceil(\delta) \subseteq max\ctx$.
\end{itemize}
Finally, as $\muconcr_{max\ctx}(\w) \neq \emptyset$, $\uconcr(\w) \neq
\emptyset$ (\pref{lem:uconcr-ctx}).
\end{proofapproxinf}
